### 2018-02-23 Paper/jaccardbaetica.tex
update material

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined somehow the system of working in the workshops. 
%habría que citar a Dressel

@@

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We analysed a dataset of 990 stamps from 81 workshops. A sample of 131 different stamps were identified and collected from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance. The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

>>>>

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the land-owners of the olive groves \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owners of the making-amphorae workshop. In any case, the use of these stamps defined somehow the system of working in the workshops. 
%habría que citar a Dressel
%olive producing

@@

Our case study examines the relation between the distribution of amphoric stamps and the workshops. We analysed a dataset of 990 stamps from 81 workshops. A sample of 131 different stamps were identified and collected from CEIPAC database (citar). The workshops were situated in different locations in Baetica province, along the river Guadalquivir and its tributary Genil in order to detect similarities between stamps from workshops and spatial distance.

The chronology in the workshops is widely diverse from I-III B.C. However, some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason can be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.
